Shader Pipeline and Effect Encapsulation using CLOS

### 2019-01-30 els2019-shader-pipeline/paper.tex
Incorporate @phoe's feedback.
Unfortunately ACM's style is fucked up and does not permit non-latin characters. For some reason, even with inputenc and bable and all that jazz Michał is not displayed correctly.

\documentclass[format=sigconf]{acmart}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[glsl]{default}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{unsrt}

@@

This function is fine for allowing the objec control over the behaviour. However, the pass cannot exert the same amount of control due to the generic function's argument precedence. We thus introduce another function with inverted argument order that is called first. \\

\code{render-with} thus exists mostly as an entry point to allow shader passes greater control over the rendering. Typically it will simply defer to \code{render}. This inversion is very important for shader passes that take all control away from the objects. Without \code{render-with}, the \code{:before}, \code{:after}, and \code{:around} methods on \code{render} specialised on an object could try to manipulate state before methods specialised on a shader pass could prevent it. \\

@@

Nevertheless, you can find the complete code online at the following pages: \\
\href{https://github.com/Shirakumo/trial/blob/b889d50b7906348ad787e773ba57998bb39b16a5/deferred.lisp}{https://github.com/Shirakumo/trial/blob/\\b889d50b7906348ad787e773ba57998bb39b16a5/deferred.lisp} \\
\href{https://github.com/Shirakumo/trial/blob/b889d50b7906348ad787e773ba57998bb39b16a5/hdr.lisp}{https://github.com/Shirakumo/trial/blob/\\b889d50b7906348ad787e773ba57998bb39b16a5/hdr.lisp} \\
\href{https://github.com/Shirakumo/trial/blob/b889d50b7906348ad787e773ba57998bb39b16a5/shadow-map.lisp}{https://github.com/Shirakumo/trial/blob/\\b889d50b7906348ad787e773ba57998bb39b16a5/shadow-map.lisp} \\
\href{https://github.com/Shirakumo/trial/blob/b889d50b7906348ad787e773ba57998bb39b16a5/workbench.lisp}{https://github.com/Shirakumo/trial/blob/\\b889d50b7906348ad787e773ba57998bb39b16a5/workbench.lisp} \\

@@

\section{Acknowledgements}\label{acknowledgements}
I would like to thank all the people that will review this paper. Your name could be here!

\section{Implementation}\label{implementation}
An implementation of the proposed system can be found at
\\\href{https://github.com/Shirakumo/trial/blob/b889d50b7906348ad787e773ba57998bb39b16a5/shader-pass.lisp}{https://github.com/Shirakumo/trial/blob/\\b889d50b7906348ad787e773ba57998bb39b16a5/shader-pass.lisp}
\\\href{https://github.com/Shirakumo/trial/blob/b889d50b7906348ad787e773ba57998bb39b16a5/pipeline.lisp}{https://github.com/Shirakumo/trial/blob/\\b889d50b7906348ad787e773ba57998bb39b16a5/pipeline.lisp}
\\\url{https://github.com/Shinmera/flow} \\

>>>>

\documentclass[format=sigconf]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[glsl]{default}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{unsrt}

@@

This function is fine for allowing the object control over the behaviour. However, the pass cannot exert the same amount of control due to the generic function's argument precedence. For example, if an \code{:around} method specialised on the object exists, a pass would not have any way of preventing it from firing, as its own \code{:around} method would be executed afterwards. We thus introduce another function with inverted argument order that is called first. \\

\code{render-with} thus exists mostly as an entry point to allow shader passes greater control over the rendering. Typically it will simply defer to \code{render}. This inversion is very important for shader passes that take all control away from the objects. \\

@@

Nevertheless, you can find the complete code online at the following pages: \\
\url{https://github.com/Shirakumo/trial/blob/b889d50/deferred.lisp} \\
\url{https://github.com/Shirakumo/trial/blob/b889d50/hdr.lisp} \\
\url{https://github.com/Shirakumo/trial/blob/b889d50/shadow-map.lisp} \\
\url{https://github.com/Shirakumo/trial/blob/b889d50/workbench.lisp} \\

@@

\section{Acknowledgements}\label{acknowledgements}
I would like to thank Michal ``phoe'' Herda, and all the people that will review this paper. Your name could be here!

\section{Implementation}\label{implementation}
An implementation of the proposed system can be found at \\
\url{https://github.com/Shirakumo/trial/blob/b889d50/shader-pass.lisp} \\
\url{https://github.com/Shirakumo/trial/blob/b889d50/pipeline.lisp} \\
\url{https://github.com/Shinmera/flow} \\
